\vspace{-15mm} \Large \textbf{Utilisation of Computer Algorithms in the Optimisation of Building Envelopes Thermal Performance}

### 2013-11-29 Paper.tex
Fri 12:39

However, as the architect approaches this method, he is faced with technical difficulties which to solve requires knowledge of computer programming, mathematical optimisation and physics. Therefore, an introduction to the process of algorithmic design of building envelopes is needed, and is the purpose of this article.

@@

>>>>

However, as the architect approaches this method, he is faced with technical difficulties which require knowledge of computer programming, mathematical optimisation and physics. Therefore, an introduction to the process of algorithmic design of building envelopes is needed, and is the purpose of this article.

@@

\paragraph{Building Modelling and Simulation}\mbox{}\\

There several methods for modelling and simulation (energy simulation) of building elements; the one discussed herein, and the most practical, is the use of Environmental/Energy Modelling and Simulatin computer programmes. There are two main advantage of these programmes:
\begin{compactenum}
	\item They save the user the hassle of modelling the physical properties and reactions of building elements into equations, which are pre-programmed in the simulation application, and measures the impact of different variables with different values on the overall thermal performance.
	\item The variable values can later on be manipulated by the optimisation algorithm to search for the optimum values through repeated simmulation of different values, thus reaching the optimum solution for each variable, or for overall optimum performance in multi-variable cases.
\end{compactenum}
